Dynamical modeling of tidal streams

### 2013-12-30 tex/ms.tex
streams: mock section

\subsection{The fiducial stream model}

@@

@@

\begin{figure}[t!]
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz.ps}
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz_sim.ps}
  \caption{Mock stream data generated from the model. The left panel
    shows the same $N$-body stream as shown in previous figures, but
    $1.96\Gyr$ earlier in its evolution. Symbols, lines, and the
    stream model are the same as those in
    \figurename~\ref{fig:gd1_xz}, except that the model progenitor
    phase-space location from \figurename~\ref{fig:gd1_xz} has been
    integrated backward in time for $1.96\Gyr$ (no other changes were
    made to the model's parameters). The right panel shows mock stream
    data drawn from the model using the procedures discussed in
    \sectionname~\ref{sec:mock}. Overall, the spatial distribution of
    the mock data is very similar to that of the $N$-body
    stream.}\label{fig:gd1_sim}
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz.ps
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz_sim.ps
\end{figure}

@@

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Carlberg(2009)]{Carlberg09a}
  Carlberg,~R.~G. 2009, \apj, 705, L223
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85a}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}

>>>>

\subsection{The fiducial stream model}\label{sec:fidmodel}

@@

\begin{figure}[t!]
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz.ps}
 \includegraphics[width=0.48\textwidth,clip=]{gd1_evol_2Gya_xz_sim.ps}
  \caption{Mock stream data generated from the model. The left panel
    shows the same $N$-body stream as shown in previous figures, but
    $1.96\Gyr$ earlier in its evolution. Symbols, lines, and the
    stream model are the same as those in
    \figurename~\ref{fig:gd1_xz}, except that the model progenitor
    phase-space location from \figurename~\ref{fig:gd1_xz} has been
    integrated backward in time for $1.96\Gyr$ and the model
    disruption time was reduced by $1.96\Gyr$ (no other changes were
    made to the model's parameters). The right panel shows mock stream
    data drawn from the model using the procedures discussed in
    \sectionname~\ref{sec:mock}. Overall, the spatial distribution of
    the mock data is very similar to that of the $N$-body
    stream.}\label{fig:gd1_mock}
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz.ps
%python plot_stream_2Gya.py ../tex/gd1_evol_2Gya_xz_sim.ps
\end{figure}

Using the generative model described in
\sectionname~\ref{sec:modeloa}, it is straightforward how to draw mock
stream data in frequency--angle space. The three ingredients---time,
frequency, and angle distributions of the debris---allow for mock data
to be generated in four steps. First, a stripping time $t_s$ is
sampled from the distribution of stripping times. Second, a frequency
offset $\Delta \veco$ with respect to the progenitor is drawn from the
frequency distribution at $t_s$. Third, an initial angle offset is
drawn. Fourth, the initial angle offset is incremented by $\Delta
\veco \,ts$. This generates the final frequency--angle coordinates of
the mock stream member $(\Delta \veco,\Delta \veca+\Delta \veco\,t_s)$.

For the fiducial stream model of \sectionname~\ref{sec:fidmodel} the
procedure for producing mock data is simplified to sampling a small
number of easy-to-sample distributions. First, $t_s$ is drawn
uniformly between $0$ and $t_d$. Second, $\Delta \operp$ is drawn from
the Gaussian distribution of $\Delta \operp$. The distribution of
$\Delta \opar$ is not Gaussian, as it is a Gaussian in $|\Delta
\opar|$ multiplied with $|\Delta \opar|$ over the range $\Delta \opar
> 0$. This distribution is log-concave, that is, the derivative of its
logarithm is negative everywhere, and therefore it can be efficienly
sampled using adaptive-rejection sampling \citep{Gilks92a}. The sign
of $\Delta \opar$ is determined by whether we are generating a leading
or trailing stream. Third, initial angle offsets are drawn from the
Gaussian distribution of such offsets.

To transform the mock stream in frequency--angle coordinates to
position--velocity space, we use the approximate procedure for this
transformation along the stream track described at the end of the
previous section. The mock stream in $(\vecx,\vecv)$ can then be
further transformed to observable coordinates
$(l,b,D,\vlos,\pmll,\pmbb)$ or any other similar quantities as
desired.

\figurename~\ref{fig:gd1_mock} shows mock data generated for the model
of the simulated stream described in
\sectionname~\ref{sec:fidmodel}. The mock data in this Figure has been
generated $1.96\Gyr$ before the final snapshot of the simulation. The
model from \sectionname~\ref{sec:fidmodel}, which was for the final
snapshot, was adjusted to this earlier time by backward orbit
integration of the model progenitor and by revising the disruption
time downward by $1.96\Gyr$. No other changes were made to the
model. The right panel of \figurename~\ref{fig:gd1_mock} shows the
mock data generated from the model in $(X,Z)$, while the left panel
shows the simulated stream data at this time. Overall, the
distribution of the mock and simulated data are similar.

@@

@@

\bibitem[{{Binney} \& {Tremaine}(2008)}]{binneytremaine}
  Binney,~J. \& Tremaine,~S. 2008, Galactic Dynamics: Second Edition
\bibitem[Binney(2008)]{Binney08a}
  Binney,~J. 2008, \mnras, 386, L47
\bibitem[Binney(2012)]{Binney12a}
  Binney,~J. 2012, \mnras, 426, 1324
\bibitem[Carlberg(2009)]{Carlberg09a}
  Carlberg,~R.~G. 2009, \apj, 705, L223
\bibitem[Carlberg(2012)]{Carlberg12a}
Carlberg,~R.~G. 2012, \apj, 748, 20
\bibitem[Dehnen(2000)]{Dehnen00a}
  Dehnen,~W. 2000, \apj, 536, L39
\bibitem[Dehnen(2002)]{Dehnen02a}
  Dehnen,~W. 2002, J.~Comput.~Phys., 179, 27
\bibitem[Eyre \& Binney(2011)]{Eyre11a}
  Eyre,~A. \& Binney,~J. 2011, \mnras, 413, 1852
\bibitem[Gilks \& Wild(1992)]{Gilks92a}
  Gilks,~W.~R. \& Wild,~P. 1992, Applied Statistics, 41, 337
\bibitem[Helmi \& White(1999)]{Helmi99a}
  Helmi,~A. \& White,~S.~D.~M. 1999, \mnras, 307, 495
\bibitem[Johnston \etal(1999)]{Johnston99a}
  Johnston,~K.~V., Zhao,~H., Spergel,~D.~N., \& Hernquist,~L. 1999, \apj, 512, L109
\bibitem[Koposov \etal(2010)]{Koposov10a}
  Koposov,~S.~E., Rix,~H.-W., \& Hogg,~D.~W. 2010, \apj, 712, 260
\bibitem[McGill \& Binney(1990)]{McGill90a}
  McGill,~C. \& Binney,~J. 1990, \mnras, 244, 634
\bibitem[McMillan \& Binney(2008)]{McMillan08a}
  McMillan,~P.~J. \& Binney,~J.~J. 2008, \mnras, 390, 429
\bibitem[Ngan \& Carlberg(2014)]{Ngan14a}
  Ngan,~W.~H.~W. \& Carlberg,~R.~G. 2014, \apj, submitted
\bibitem[Pe{\~n}arrubia \etal(2012)]{Penarrubia12a}
  Pe{\~n}arrubia, J., Koposov,~S.~E., \& Walker,~M.~G. 2012, \apj, 760, 2
\bibitem[Price-Whelan \& Johnston(2013)]{PriceWhelan13a}
  Price-Whelan,~A.~M. \& Johnston,~K.~V.~2013, \apj, 778, L12
\bibitem[Sanders(2012)]{Sanders12a}
  Sanders,~J. 2012, \mnras, 426, 128
\bibitem[Sanders \& Binney(2013a)]{Sanders13a}
  Sanders,~J. \& Binney,~J. 2013a, \mnras, 433, 1813
\bibitem[Sanders \& Binney(2013b)]{Sanders13b}
  Sanders,~J. \& Binney,~J. 2013b, \mnras, 433, 1826
\bibitem[Shoemake(1985)]{Shoemake85a}
  Shoemake,~K. 1985, ACM SIGGRAPH Computer Graphics 3, 45
\bibitem[Teuben(1995)]{Teuben95a}
  Teuben,~P.~J. 1995, in Astronomical Data Analysis Software and Systems IV, 
  ed.~R.~Shaw, H.~E.~Payne and J.~J.~E.~Hayes., PASP Conf Series 77, 398
\bibitem[Tremaine(1999)]{Tremaine99a}
  Tremaine,~S. 1999, \mnras, 307, 877
\bibitem[Yoon \etal(2011)]{Yoon11a}
  Yoon,~J.~H., Johnston,~K.~V., \& Hogg,~D.~W. 2011, \apj, 731, 58
\end{thebibliography}
